Universal relations after GW170817

### 2019-01-02 paper/bin-love-after-gw170817.tex
Added C-Love section to the paper

\title{Universal relations after GW170817\kc{Here and elsewhere: I suggest we use the term "EoS-insensitive" instead of "universal" relations}}

@@

\author{Katerina Chatziioannou}
%\affiliation{%
% Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
%}%
\affiliation{%
 Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% Intro
The thermodynamic relationship between pressure and density (the equation of state) of \kc{cold} supranuclear matter, accessible primarily in neutron stars\kc{this statement makes nuclear experiment people not happy}, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date. 
% How to probe
The extraction of tidal deformabilities from the gravitational waveforms of binary neutron star merger events, such as GW170817, is a promising method of probing the nuclear structure.
% What was done before - Binary Love
Previous studies have shown that approximately equation of state insensitive ``binary Love universal relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
% What was done before - I-Love-Q
Similarly, another set of equation of state \sout{independent}\kc{insensitive} relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), and quadrupole moment (Q) - known as the ``I-Love-Q universal relations."
% What universal relations do
Such universal relations\kc{so far we have said "EoS-insensitive", "EoS-independent", and "universal". We should pick a name and stick with it. I suggest "EoS-insensitive"} allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation\kc{You mean $\tilde{\Lambda}$? In our paper with Carl and Aaron we showed that the binary Love relation doesn't affect the $\tilde{\Lambda}$ measurement much.}.
% What we will do
\kc{Add a sentence saying that even the more precise relations have some EoS variation which can cause a systematic error which can be marginalized over}
In this document, we explain how one can reduce equation of state variation for both binary Love and I-Love-Q universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers\kc{but we show that the systematic effects of these relations is very small until next-G detectors.}. 
We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
% What we found
We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, and in I-Love-Q universality by factors of $\sim 50$\%.
% Conclude
We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.\kc{We should give the answer to this here: Yes!}
\end{abstract}

@@

\section{Introduction}\label{sec:intro}
%Intro
The dependence of pressure on density for \kc{cold} supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
Unfortunately, terrestrial experiments can only study the EoS up to the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}, making NSs ideal laboratories for constraining ultra dense nuclear matter\kc{heavy ion collisions supposedly go to higher densities, but they are T-dependent}.

%Constraining the EoS
Independent measurements of NS observables can be used to constrain the nuclear EoS.
For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on NSs\kc{limits on what?}~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
However, these implications \kc{potentially} suffer from large systematic errors due to uncertainties in the astrophysical modeling \kc{of...}.
Alternatively, the emission of gravitational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
During the early inspiral portion of the merger, the orbital separation is large enough that the effect of companion tidal fields is negligible. 
As the separation decreases through GW emission, tidal forces are magnified and the NSs deform from sphericity, altering the orbital trajectories; a relic which is directly imprinted on the GW signal.
This deformation is characterized by the \textit{tidal deformability} $\Lambda$ as the linear response of the NSs quadrupole moment $Q_{ij}$ to the neighboring tidal field $\varepsilon_{ij}$~\cite{hinderer-love,Flanagan2008}.

%reparameterization of the template
In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering in the gravitational waveform\cite{Flanagan2008,Vines:2011ud}.
Due to high correlations between between the two parameters, independent extraction becomes very difficult at current interferometer sensitivities~\cite{Wade:tidalCorrections}.
Typically, these high correlations can be reduced by strategically reparameterizing the waveform template with new tidal parameters constructed from linear combinations of $\Lambda_1$ and $\Lambda_2$.
For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{Favata:2013rwa,Wade:tidalCorrections} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.

%Universal relations
Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability\kc{That's the first time I hear this term!}.
Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model\kc{decrease in uncertainty in which parameter?}, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first~\cite{Katerina:residuals}.  
Use of this relations leads to up to an order of magnitude improvement in parameter estimation \kc{of what?} through a simple Fisher analysis~\cite{Yagi:binLove}, also confirmed with the detailed analysis of~\cite{Katerina:residuals}.
Similar ``I-Love-Q" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, and tidal deformability; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.

\kc{Say here that these relations are tuned to many EoS models and have intrinsic uncertainties. }
%How we improved this
In this analysis, we aim to improve this important work by imposing the restrictions found on the EoS~\cite{LIGO:posterior} derived from the recent binary NS merger observation, GW170817~\cite{TheLIGOScientific:2017qsa}.
By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for both binary Love and I-Love-Q universal relations.
In addition, we consider hybrid star EoSs seen in~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter.
These provide a departure from the nuclear matter relations considered here - providing valuable insight into them.
Further, we estimate the viability of using improved universal relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.

\subsection{Executive Summary}
\kc{The paper is fairly short, is the summary here necessary?}

%What we did
In this paper we attempt to improve binary Love and I-Love-Q universal relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
In addition, we determine the degree to which hybrid star EoSs obey binary Love universal relations.
Finally, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Unfortunately\kc{??}, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}\kc{a\texttt{++} should be A\texttt{+}}.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$)\kc{How are we combining the uncertainty on $\tilde{\Lambda}$ when each event will have a different $\tilde{\Lambda}$?}.
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable\kc{viable? you mean necessary?}.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year \kc{Instead of points, it might be clearer to show this with shaded regions from the upper to the lower rate.}.
It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
Note there is no simulated populations of events under the O2 design sensitivity - due to there only being a single event during the observing period.
These results are further tabulated in Table~\ref{tab:variances}.
}
\label{fig:stackedFisher}
\end{figure}

%outline
The organization of this paper is outlined below.
We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love and I-Love-Q universal relations, and considering how well hybrid star EoSs agree with the universal relations.
We next examine these improved universal relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
Throughout this paper, we have adopted geometric units of $G=c=1$, unless otherwise stated.

@@

\subsubsection{Nuclear matter stars}\label{sec:ilq-nuc}
Following the work of Ref.~\cite{Yagi:ILQ}, the data for each universal relation is first fit to the following curve:
\begin{equation}\label{eq:ILQfit}
\ln{y_i}=a_i+b_i \ln{x_i} + c_i (\ln{x_i})^2 + d_i (\ln{x_i})^3 + e_i (\ln{x_i})^4,
\end{equation}
where the updated coefficients are given in Table~\ref{tab:ILQfit}.
Additionally, we offer an improvement to the functional form of the I-Love-Q fitting curve. 
Namely, we use the Newtonian relationships between various observables as a controlling factor in the fit~\cite{Yagi:ILQ}:
\begin{equation}\label{eq:Newtonian}
\bar{I}^{\text{N}} = C_{\bar{I}\Lambda}\Lambda^{2/5}, \hspace{3mm} \bar{Q}^{\text{N}} = C_{\bar{Q}\Lambda}\Lambda^{1/5}, \hspace{3mm} \bar{I}^{\text{N}} = C_{\bar{I}\bar{Q}}\bar{Q}^{2}.
\end{equation}
This is appended to an expansion in $\Lambda^{-1/5} \propto C$ (or $\bar{Q}^{-1/5}$), where $C=M/R$ is the compactness of the star.
This results in the following overall fitting relation:
\begin{equation}\label{eq:ILQfitNew}
y=C_{yx} x^{\alpha} \frac{1+\sum_{i=1}^3 a_i x^{-i/5}}{1+\sum_{i=1}^3 b_i x^{-i/5}},
\end{equation}
where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and $\alpha$ is given by $2/5$, $1/5$, and $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations, respectively.
The new fitting coefficients are presented in Table~\ref{tab:ILQfitNew}.
While the two above fits both result in fits with similar $R^2$ values of $\sim 0.9999995$ for the data presented, the lattter one has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.

@@

\begin{table*}
\centering
\caption{
I-Love-Q universal relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
}\label{tab:ILQfitNew}
\begin{tabular}{ c  c  | c c c c c c c c} 
 \hline
 \hline
 $y$ & $x$ & $\alpha$ & $C_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313031$ & $1.2868285$ & $0.0988787$ & $-2.3001034$ & $-1.3465945$ & $0.3857349$ & $-0.0287014$\\
 $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.5554627$ & $-2.1218079$ & $2.7237378$ & $-1.4906808$ & $0.8643535$ & $-0.1427541$ & $-1.3973147$\\
 $\bar{I}$ & $\bar{Q}$ & $2$ & $0.0089212$ & $10.5910815$ & $-37.4581345$ & $43.1831156$ & $-2.3610288$ & $1.9674667$ & $-0.5678018$\\
\hline
\hline
\end{tabular}
\end{table*}

@@

>>>>

\title{Universal relations after GW170817}

@@

\author{Katerina Chatziioannou}
\affiliation{%
 Canadian Institute for Theoretical Astrophysics, 60 St. George Street, Toronto, Ontario, M5S 3H8, Canada
}%
\affiliation{%
 Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010
}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% Intro
The thermodynamic relationship between pressure and density (the equation of state) of supranuclear matter, accessible primarily in neutron stars, is critical to the study of such stars, and is one of the largest uncertainties in nuclear physics to date. 
% How to probe
The extraction of tidal deformabilities from the gravitational waveforms of binary neutron star merger events, such as GW170817, is a promising method of probing the nuclear structure.
% What was done before - Binary Love
Previous studies have shown that approximately equation of state insensitive ``binary Love universal relations" exist between symmetric and antisymmetric combinations of individual tidal deformabilities, which are difficult to be independently measured with second-generation gravitational wave interferometers.
% What was done before - I-Love-Q
Similarly, another set of equation of state independent relations exist between individual neutron star parameters: moment of inertia (I), tidal deformability (Love number), quadrupole moment (Q), and compactness (C) - known as the ``I-Love-Q" and ``C-Love" universal relations.
% What universal relations do
Such universal relations allow the elimination of some tidal parameters from the list of model parameters, thus breaking degeneracies and ultimately reducing the uncertainty of the dominant tidal effect in parameter estimation.
% What we will do
In this document, we explain how one can reduce equation of state variation for binary Love, I-Love-Q, and C-Love universal relations, which helps to reduce systematic errors on the tidal measurement of binary neutron star mergers. 
We achieve this  by restricting to only equations of state drawn from the 90\% posterior constraint on pressure as a function of density, as derived by the LIGO Collaboration.
% What we found
We find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with a mass ratio of 0.75, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim 50$\%.
% Conclude
We end by comparing systematic errors on tidal measurement due to the equation of state variation with statistical errors and comment on whether one can safely use these universal relations with future gravitational wave observations.
\end{abstract}

@@

\section{Introduction}\label{sec:intro}
%Intro
The dependence of pressure on density for supranuclear matter found primarily inside neutron stars (NSs) remains to be one of the largest mysteries in both nuclear physics and astrophysics.
This internal structure of such stars, known as the equation of state (EoS), is exceedingly important, as it is the determining factor for many NS observables - such as the mass, the radius, and many more.
Unfortunately, terrestrial experiments can only study the EoS up to the nuclear saturation density ($\rho_{\text{sat}} \approx 2.5 \times 10^{14} \text{ g/cm}^3$)~\cite{Li:HeavyIon,Tsang:SymmetryEnergy,Centelles:NeutronSkin,Li:CrossSections,Chen:SymEnergy}, making NSs ideal laboratories for constraining ultra dense nuclear matter.

%Constraining the EoS
Independent measurements of NS observables can be used to constrain the nuclear EoS.
For example, electromagnetic observations of the mass-radius relationship of NSs have been used to place limits on NSs~\cite{guver,ozel-baym-guver,steiner-lattimer-brown,Lattimer2014,Ozel:2016oaf}.
However, these implications suffer from large systematic errors due to astrophysical mismodeling.
Alternatively, the emission of gravitational waves (GWs) from binary NS merger events have proven to be a unique method of probing nuclear physics.
During the early inspiral portion of the merger, the orbital separation is large enough that the effect of companion tidal fields is negligible. 
As the separation decreases through GW emission, tidal forces are magnified and the NSs deform from sphericity, altering the orbital trajectories; a relic which is directly imprinted on the GW signal.
This deformation is characterized by the \textit{tidal deformability} $\Lambda$ as the linear response of the NSs quadrupole moment $Q_{ij}$ to the neighboring tidal field $\varepsilon_{ij}$.

%reparameterization of the template
In the case of binary NSs, each star becomes deformed via the process highlighted above, resulting in two highly correlated tidal parameters $\Lambda_1$ and $\Lambda_2$ entering in the gravitational waveform.
Due to high correlations between between the two parameters, independent extraction becomes very difficult at current interferometer sensitivities.\zc{cite?}
Typically, these high correlations can be reduced by strategically reparameterizing the waveform template with new tidal parameters constructed from linear combinations of $\Lambda_1$ and $\Lambda_2$.
For example, utilizing the parameters $\tilde{\Lambda}$ and $\delta \tilde{\Lambda}$~\cite{hinderer-love,Flanagan2008} which enter the GW waveform at different post-Newtonian (PN) orders (powers of the ratio between the orbital speed and the speed of light $v/c^{2n}$) partially mitigates these correlations.

%Universal relations
Unfortunately, current detectors are only sensitive enough to accurately measure the dominant tidal parameter, $\tilde{\Lambda}$, known as the chirp deformability.
Previous work by Yagi and Yunes~\cite{Yagi:binLove} resolved this issue by finding approximately EoS-insensitive ``binary Love universal relations" between symmetric and anti-symmetric combinations of tidal deformabilities $\frac{1}{2}(\Lambda_1 \pm \Lambda_2)$.
This allows one to further break degeneracies between tidal parameters, resulting in both (i) a decrease in uncertainty upon parameter extraction on the removal of one parameter from the model, and (ii) the ability to measure the secondary tidal parameter upon measurement of the first.  
This important work showed up to an order of magnitude improvement in parameter estimation through a simple Fisher analysis.
Similar ``I-Love-Q" and ``C-Love" universal relations~\cite{Yagi:ILQ} have been found between individual NS observables: quadrupole moment , moment of inertia, tidal deformability, and compactness; similarly allowing the removal of tidal parameters from the model list, and allowing an automatic determination of one observable through the measurement of another.

%How we improved this
In this analysis, we aim to improve this important work by imposing the restrictions found on the EoS~\cite{LIGO:posterior} derived from the recent binary NS merger observation, GW170817~\cite{TheLIGOScientific:2017qsa}.
By restricting to only EoSs which lie within the the 90\% credible region on pressure as a function of density found in~\cite{LIGO:posterior}, we repeat the analyses done in~\cite{Yagi:binLove,Yagi:ILQ} and show an increase in universality for both binary Love and I-Love-Q universal relations.
In addition, we consider hybrid star EoSs seen in~\cite{Paschalidis2018}, which experience strong first-order transitions from hadronic matter to quark matter.
These provide a departure from the nuclear matter relations considered here - providing valuable insight into them.
Further, we estimate the viability of using improved universal relations on future GW detections by performing simple Fisher analyses to approximate when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.

\subsection{Executive Summary}
%What we did
In this paper we attempt to improve binary Love and I-Love-Q universal relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
In addition, we determine the degree to which hybrid star EoSs obey such universal relations.
Finally, through a simple Fisher analysis, we consider the value in improving universal relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in universal relations.

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (red) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper (teal), central (orange), and lower (magenta) limits of expected binary NS merger detection rates for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observation year.
It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (purple shaded region) for Voyager and on.
Note there is no simulated populations of events under the O2 design sensitivity - due to there only being a single event during the observing period.
These results are further tabulated in Table~\ref{tab:variances}.
}
\label{fig:stackedFisher}
\end{figure}

%outline
The organization of this paper is outlined below.
We begin with a complementary background and theory material in Sec.~\ref{sec:theory}.
We continue in Sec.~\ref{sec:universal} by finding new and improved binary Love, I-Love-Q, and C-Love universal relations, and considering how well hybrid star EoSs agree with the universal relations.
We next examine these improved universal relations and question whether or not they are useful for future interferometers in Sec.~\ref{sec:observations}.
We conclude in Sec.~\ref{sec:conclusion} by discussing our results and mentioning avenues of future work.
Throughout this paper, we have adopted geometric units of $G=c=1$, unless otherwise stated.

@@

\subsubsection{Nuclear matter stars}\label{sec:ilq-nuc}
Following the work of Ref.~\cite{Yagi:ILQ}, the data for each universal relation is first fit to the following curve:
\begin{equation}\label{eq:ILQfit}
\ln{y_i}=a_i+b_i \ln{x_i} + c_i (\ln{x_i})^2 + d_i (\ln{x_i})^3 + e_i (\ln{x_i})^4,
\end{equation}
where the updated coefficients are given in Table~\ref{tab:ILQfit}.
Additionally, we offer an improvement to the functional form of the I-Love-Q fitting curve. 
Namely, we use the Newtonian relationships between various observables as a controlling factor in the fit~\cite{Yagi:ILQ}:
\begin{equation}\label{eq:Newtonian}
\bar{I}^{\text{N}} = C_{\bar{I}\Lambda}\Lambda^{2/5}, \hspace{3mm} \bar{Q}^{\text{N}} = C_{\bar{Q}\Lambda}\Lambda^{1/5}, \hspace{3mm} \bar{I}^{\text{N}} = C_{\bar{I}\bar{Q}}\bar{Q}^{2}.
\end{equation}
This is appended to an expansion in $\Lambda^{-1/5} \propto C$ (or $\bar{Q}^{-1/5}$), where $C=M/R$ is the compactness of the star.
This results in the following overall fitting relation:
\begin{equation}\label{eq:ILQfitNew}
y=C_{yx} x^{\alpha} \frac{1+\sum_{i=1}^3 a_i x^{-i/5}}{1+\sum_{i=1}^3 b_i x^{-i/5}},
\end{equation}
where $y$ and $x$ correspond to NS observables $\bar{I}$, $\bar{Q}$, and $\Lambda$, and $\alpha$ is given by $2/5$, $1/5$, and $2$ for the $\bar{I}-\Lambda$, $\bar{Q}-\Lambda$, and $\bar{I}-\bar{Q}$ relations, respectively.
The new fitting coefficients are presented in Tab.~\ref{tab:ILQfitNew}.
While the two above fits both result in fits with similar $R^2$ values of $\sim 0.9999995$ for the data presented, the lattter one has the advantage that it properly limits to the Newtonian case as $\Lambda \rightarrow \infty$~\cite{Yagi:binLove}.

@@

\begin{table*}
\centering
\caption{
I-Love-Q and C-Love universal relations fit parameters for the constrained EoS data using the improved fitting relations found in Eq.~\ref{eq:ILQfitNew}.
This fitting relation, unlike previous versions, properly limits to the Newtonian case as $\Lambda \rightarrow \infty$.
}\label{tab:ILQfitNew}
\begin{tabular}{ c  c  | c c c c c c c c} 
 \hline
 \hline
 $y$ & $x$ & $\alpha$ & $C_{yx}$ & $a_1$ & $a_2$ & $a_3$ & $b_1$ & $b_2$ & $b_3$ \\
 \hline
 $\bar{I}$ & $\Lambda$ & $2/5$ & $0.5313031$ & $1.2868285$ & $0.0988787$ & $-2.3001034$ & $-1.3465945$ & $0.3857349$ & $-0.0287014$\\
 $\bar{Q}$ & $\Lambda$ & $1/5$ & $3.5554627$ & $-2.1218079$ & $2.7237378$ & $-1.4906808$ & $0.8643535$ & $-0.1427541$ & $-1.3973147$\\
 $\bar{I}$ & $\bar{Q}$ & $2$ & $0.0089212$ & $10.5910815$ & $-37.4581345$ & $43.1831156$ & $-2.3610288$ & $1.9674667$ & $-0.5678018$\\
 $\bar{C}$ & $\Lambda$ & $-1/5$ & $0.2495709$ & $-919.5651942$ & $330.2848184$ & $-857.1842107$ & $-383.5404843$ & $192.4933832$ & $-811.1425435$\\
\hline
\hline
\end{tabular}
\end{table*}

@@

\subsection{C-Love Relations}\label{sec:clove}
In this section we consider approximate C-Love universal relations between NS compactness $\bar{C} \equiv M/R$ and unitless tidal deformability $\Lambda$, as discussed by Yagi and Yunes~\cite{Yagi:binLove}.
Similar to the previous section, we consider two classes of stars: nuclear matter EoSs and hybrid quark-hadron star EoSs.

\subsubsection{Nuclear matter stars}\label{sec:clove-nuc}
Following Ref.~\cite{Yagi:binLove}, we begin by fitting the data for each set of EoSs to the simple curve:
\begin{equation}
\bar{C} = \sum^2_{k=0} a_k (\ln{\Lambda})^k.
\end{equation}
Doing so yields $a_0 = 0.3616998$, $a_1 = -0.0354818$, and $a_2 = 0.0006193849$, similar to what was found in Ref.~\cite{Yagi:binLove}.
Additionally we offer an improvement to the fits as was done in Sec.~\ref{sec:ilq}. 
We consider the fitting function found in Eq.~\ref{eq:ILQfitNew}, with the controlling factor given by:
\begin{equation}
\bar{C}^N=C_{\bar{C}\Lambda}\Lambda^{-1/5}.
\end{equation}
The new fitting coefficients are displayed in Tab.~\ref{tab:ILQfitNew}, alongside the previously found I-Love-Q relations.

Figure~\ref{fig:clove} presents the C-Love universal relations for both the constrained and unconstrained sets of EoSs, along with the relative fractional difference from the fits. 
Observe how the constrained EoSs show a large suppression in EoS variability compared to both the unconstrained EoSs, as well as that found in previous works~\cite{Yagi:binLove}.
The maximal EoS variation is compared between the above three cases in Tab.~\ref{tab:maxVar}.
\begin{figure}
\begin{center} 
\includegraphics[width=1\columnwidth]{CL.eps}
\end{center}
\caption{
Similar to Fig.~\ref{fig:ILQ} but for C-Love universal relations.
In this figure, we similarly construct fits to  Eq.~\ref{eq:ILQfitNew}, properly limiting to the newtonian case $\bar{C} \sim \Lambda^{-1/5}$.
Observe how, as before, the fractional difference from the fits is greatly suppressed for the constrained case, compared to both the unconstrained case, and results from previous works~\cite{Yagi:binLove}.
The maximal EoS variation from the fits for the unconstrained and constrained sets of EoSs are compared in Tab.~\ref{tab:maxVar}.
Additionally shown in this figure is the hybrid star C-Love relations along with their fractional difference from the constrained EoS fits (dashed green).
}
\label{fig:clove}
\end{figure}

These results, similar to that found in Sec.~\ref{sec:ilq}, show the considerable improvement found in using constrained EoSs over any unconstrained set.
We also note that the unconstrained EoSs display slightly larger EoS variability than found in Ref.~\cite{Yagi:binLove}, due to the large random sampling as discussed previously in Sec.~\ref{sec:ilq}.

\subsubsection{Hybrid quark-hadron stars}\label{sec:clove-hyb}
In this section, we consider the effect of hybrid star EoSs on the C-Love universal relation.
Much like Sec.~\ref{sec:ilq-hyb}, we perform 3 separate fits (constrained and hybrid EoSs combined, constrained EoSs only, and hybrid EoSs only) and compare the maximal EoS variation for each class of EoSs.

Table~\ref{tab:hybridCompareClove} compares the maximal EoS variability for the constrained and hybrid star EoSs under the fitting conditions for each case described above. 
We observe very similar behavior to that described in Sec.~\ref{sec:ilq-hyb}, in which the maximal EoS variation for hybrid stars only fluctuate slightly ($\sim 4.5\% - 7\%$) for each case.
From this, we similarly conclude that hybrid stars do obey the C-Love universal relation derived with nuclear matter stars, with the caveat that the maximum universality increases to $\sim 7.1\%$.
This is exemplified in Fig.~\ref{fig:clove} by the dashed green curves.
